---
title: "gabovicen_OriginalHomeworkCode_01"
author: "Gabo"
date: "9/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Original Homework Code



```{r instructions}
```

First, create a vector of 1, word character strings comprising the first line of the novel Ulysses, by James Joyce: “Stately, plump Buck Mulligan came from the stairhead, bearing a bowl of lather on which a mirror and a razor lay crossed.”

Then, extract every third element of this vector.

## Challenge 1

```{r}
Vector_1<- c("Stately","plump", "Buck","Mulligan", "came", "from", "the", "stairhead", "bearing", "a", "bowl", "of", "lather", "on", "which", "a", "mirror", "and", "a", "razor", "lay", "crossed")
Vector_2<-Vector_1[seq(1,22, by=3)]
Vector_2
```

## Chalenge 2

```{r}
m <- matrix(data = 1:80, nrow = 8, ncol = 10, byrow = FALSE)
m
```


Given the matrix, m, extract the 2nd, 3rd, and 6th columns and assign them to the variable x.

Given the matrix, m, above, extract the 6th to 8th row and assign them to the variable x.

Given the matrix, m, above, extract the elements from row 2, column 2 to row 6, column 9 and assign them to the variable x.


```{r}
x<-m[,c(2,3,6)]
x
```
```{r}
x<-m[6:8]
x
```
```{r}
x<-m[2:6,2:9]
x
```

## Chalenge 3

Construct a 4-dimensional, 400 element array (5 x 5 x 4 x 4) named a consisting of the numbers 400 to 1.

```{r}
a<-array(400:1, c(5,5,4,4))
a
```

1) a[1, 1, 1, 2]

```{r}
a[1, 1, 1, 2]
```

2) a[2, 3, 2, ]

```{r}
a[2, 3, 2, ]
```

3) a[1:5, 1:5, 3, 3]

```{r}
a[1:5, 1:5, 3, 3]
```

## Chalenge 4

Create a list representing this (simplified) primate taxonomy:

```{r}
Platyrrhini <- c("Cebidae", "Atelidae", "Pitheciidae")
Catarrhini <-c("Cercopithecidae", "Hylobatidae", "Hominidae")
Anthropoidea <- list(Platyrrhini, Catarrhini)
names(Anthropoidea) <- list("Platyrrhini", "Catarrhini")
Anthropoidea
Tarsioidea <-c("Tarsiidae")
Tarsioidea
Haplorhini <- list(Anthropoidea, Tarsioidea)
names(Haplorhini) <-list("Anthropoidea", "Tarsioidea")
Haplorhini
Primates <-list(Haplorhini, Strepsirhini)
names(Primates) <-list("Haplorhini", "Strepsirhini")
Primates
```

## Chalenge 5

```{r}
m3 <- matrix(data = c(3, 0, 1 ,23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2), nrow = 5, ncol = 3, byrow = TRUE)
m3
df<- as.data.frame (m3, row.names = NULL, optional = FALSE)
as.logical(df$V2)
as.factor(df$V3)
str(df)
```

