---
title: "gabovicen_OriginalHomeworkCode_01"
author: "Gabo"
date: "9/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Original Homework Code
## Frank Short Peer Commentary



```{r instructions}
```

First, create a vector of 1, word character strings comprising the first line of the novel Ulysses, by James Joyce: “Stately, plump Buck Mulligan came from the stairhead, bearing a bowl of lather on which a mirror and a razor lay crossed.”

Then, extract every third element of this vector.

## Challenge 1

```{r}
# Something went wrong when knitting in your markdown, and the results from the code do not show up in the html file.

Vector_1<- c("Stately","plump", "Buck","Mulligan", "came", "from", "the", "stairhead", "bearing", "a", "bowl", "of", "lather", "on", "which", "a", "mirror", "and", "a", "razor", "lay", "crossed")
Vector_2<-Vector_1[seq(1,22, by=3)]
Vector_2

# You can also use the stringr package to enter the full sentence as a character string, and then delineate each character by a space. 
```

## Challenge 2

```{r}
m <- matrix(data = 1:80, nrow = 8, ncol = 10, byrow = FALSE)
m
```


Given the matrix, m, extract the 2nd, 3rd, and 6th columns and assign them to the variable x.

Given the matrix, m, above, extract the 6th to 8th row and assign them to the variable x.

Given the matrix, m, above, extract the elements from row 2, column 2 to row 6, column 9 and assign them to the variable x.


```{r}
# It might be a good idea to put the instruction before each part you're doing. (IE: 2nd, 3rd, and 6th for the one bellow, etc.)
x<-m[,c(2,3,6)]
x
```
```{r}
x<-m[6:8]
x
```

```{r}
x<-m[2:6,2:9]
x
```

## Challenge 3

Construct a 4-dimensional, 400 element array (5 x 5 x 4 x 4) named a consisting of the numbers 400 to 1.

```{r}
a<-array(400:1, c(5,5,4,4))
a
```

1) a[1, 1, 1, 2]

```{r}
a[1, 1, 1, 2]
```

2) a[2, 3, 2, ]

```{r}
a[2, 3, 2, ]
```

3) a[1:5, 1:5, 3, 3]

```{r}
a[1:5, 1:5, 3, 3]
```

## Challenge 4

Create a list representing this (simplified) primate taxonomy:

```{r}
Platyrrhini <- c("Cebidae", "Atelidae", "Pitheciidae")
Catarrhini <-c("Cercopithecidae", "Hylobatidae", "Hominidae")
Anthropoidea <- list(Platyrrhini, Catarrhini)
names(Anthropoidea) <- list("Platyrrhini", "Catarrhini")
Anthropoidea
Tarsioidea <-c("Tarsiidae")
Tarsioidea
Haplorhini <- list(Anthropoidea, Tarsioidea)
names(Haplorhini) <-list("Anthropoidea", "Tarsioidea")
Haplorhini

# Need to make Strepsirhini with Lemoroidea and Lorisoidea nested in it first.

Primates <-list(Haplorhini, Strepsirhini)

# Error since Strepsirhini is not yet an object created.

names(Primates) <-list("Haplorhini", "Strepsirhini")
Primates
```

## Challenge 5


```{r}
# Instructions above?
m3 <- matrix(data = c(3, 0, 1 ,23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2), nrow = 5, ncol = 3, byrow = TRUE)
m3
df<- as.data.frame (m3, row.names = NULL, optional = FALSE)
as.logical(df$V2)
as.factor(df$V3)
str(df)
#V2 and V3 are not logical and factor values respectively as shown by str. You can force these columns to be reflected as those types of values by using the method laid out in the Overwriting section of Module 4 (Atleast that's how I did it.)
```

